The Proofs

### 2023-11-13 proofs/tex/unif-constraint-merge-lemmas.tex
Add Declarative Typing comments
Restructure proofs

\begin{observation} [Unification Constraint Merge is Deterministic]
    \label{obs:unif-merge-deterministic}
    Suppose that $[[Θ ⊢ UC1]]$ and $[[Θ ⊢ UC2]]$
    If $[[Θ ⊢ UC1 & UC2 = UC]]$ and $[[Θ ⊢ UC1 & UC2 = UC']]$ are defined then 
    $[[UC]] = [[UC']]$.
\end{observation}
\begin{proof}
    $[[UC]]$ and $[[UC']]$ both consists of three parts: 
    Entries of $[[UC1]]$ that do not have matching entries in $[[UC2]]$,
    entries of $[[UC2]]$ that do not have matching entries in $[[UC1]]$,
    and the merge of matching entries.

@@

\begin{lemma} [Soundness of Unification Constraint Merge]
    \label{lemma:unif-merge-soundness}
    Suppose that $[[Θ ⊢ UC1]]$ and $[[Θ ⊢ UC2]]$ 
    are normalized unification constraints.
    If $[[Θ ⊢ UC1 & UC2 = UC]]$ is defined then
    $[[UC = UC1 ∪ UC2]]$.
\end{lemma}
\begin{proof}
    \hfill
    \begin{itemize}
        \item $[[UC1 & UC2]] \subseteq [[UC1]] \cup [[UC2]]$\\
        By definition, 
        $[[UC1 & UC2]]$ consists of three parts:
        entries of $[[UC1]]$ that do not have matching entries of $[[UC2]]$,
        entries of $[[UC2]]$ that do not have matching entries of $[[UC1]]$,
        and the merge of matching entries.

@@

\begin{corollary}
    \label{corollary:unif-merge-soundness}
    Suppose that $[[Θ ⊢ UC1]]$ and $[[Θ ⊢ UC2]]$ 
    are normalized unification constraints.
    If $[[Θ ⊢ UC1 & UC2 = UC]]$ is defined then
    \begin{enumerate}
        \item $[[Θ ⊢ UC]]$ is normalized unification constraint,
        \item for any substitution $[[Θ ⊢ uσ : dom(UC)]]$, $[[ Θ  ⊢ uσ : lift UC ]]$ implies 
        $[[ Θ ⊢ uσ : lift UC1 ]]$ and $[[Θ ⊢ uσ : lift UC2]]$.
    \end{enumerate}
\end{corollary}
\begin{proof}
    It is clear that since $[[UC = UC1 ∪ UC2]]$ (by \cref{lemma:unif-merge-soundness}),
    and being normalized means that all entries are normalized,
    $[[UC]]$ is a normalized unification constraint.
    Analogously, $[[Θ ⊢ UC]] = [[UC1 ∪ UC2]]$ holds immediately, 
    since $[[Θ ⊢ UC1]]$ and $[[Θ ⊢ UC2]]$.

@@

\begin{lemma} [Completeness of Unification Constraint Entry Merge]
    \label{lemma:unif-entry-merge-completeness}
    For a fixed context $[[Γ]]$,
    suppose that $[[Γ ⊢ ucE1]]$ and $[[Γ ⊢ ucE2]]$ are matching constraint entries.
    \begin{itemize}
        \item for a type $[[iP]]$ such that $[[Γ ⊢ iP : ucE1]]$ and $[[Γ ⊢ iP : ucE2]]$,
        $[[Γ ⊢ ucE1 & ucE2 = ucE]]$ is defined and $[[Γ ⊢ iP : ucE]]$.
        \item for a type $[[iN]]$ such that $[[Γ ⊢ iN : ucE1]]$ and $[[Γ ⊢ iN : ucE2]]$,
        $[[Γ ⊢ ucE1 & ucE2 = ucE]]$ is defined and $[[Γ ⊢ iN : ucE]]$.
    \end{itemize}
\end{lemma}
\begin{proof}
    Let us consider the shape of $[[ucE1]]$ and $[[ucE2]]$.
    \begin{caseof}
        \item $[[ucE1]]$ is $[[pua :≈ iQ1]]$ and $[[ucE2]]$ is $[[pua :≈ iQ2]]$.
            Then $[[Γ ⊢ iP : ucE1]]$ means $[[Γ ⊢ iP ≈ iQ1]]$, 
            and $[[Γ ⊢ iP : ucE2]]$ means $[[Γ ⊢ iP ≈ iQ2]]$.
            Then by transitivity of equivalence (\cref{corollary:equivalence-transitivity}),
            $[[Γ ⊢ iQ1 ≈ iQ2]]$, which means $[[nf(iQ1) = nf(iQ2)]]$ by
            \cref{lemma:subt-equiv-algorithmization}.
            Hence, \ruleref{\ottdruleSCMEPEqEqLabel} applies to infer
            $[[Γ ⊢ ucE1 & ucE2 = ucE2]]$, and $[[Γ ⊢ iP : ucE2]]$ holds by assumption.
        \item $[[ucE1]]$ is $[[nua :≈ iN1]]$ and $[[ucE2]]$ is $[[nua :≈ iM2]]$.
            The proof is symmetric.
    \end{caseof}
\end{proof}

\begin{lemma} [Completeness of Unification Constraint Merge] 
    \label{lemma:unif-merge-completeness}
    Suppose that $[[Θ ⊢ UC1]]$ and $[[Θ ⊢ UC2]]$.
    Then for any $[[Ξ]] \supseteq [[dom(UC1) ∪ dom(UC2)]]$ 
    and substitution $[[Θ ⊢ uσ : Ξ]]$ such that $[[ Θ ⊢ uσ : lift UC1 ]]$ and $[[ Θ   ⊢ uσ : lift UC2 ]]$, 
    \begin{enumerate}
        \item $[[Θ ⊢ UC1 & UC2 = UC]]$ is defined and
        \item $[[ Θ   ⊢ uσ : UC ]]$.
    \end{enumerate}
\end{lemma}
\begin{proof}
    The proof repeats the proof of \cref{lemma:merge-completeness}
    for cases 
    uses \cref{lemma:unif-entry-merge-completeness} instead of \cref{lemma:entry-merge-completeness}.
\end{proof}

>>>>

\obsUnifMergeDet*
\begin{proof}
    $[[UC]]$ and $[[UC']]$ both consists of three parts: 
    Entries of $[[UC1]]$ that do not have matching entries in $[[UC2]]$,
    entries of $[[UC2]]$ that do not have matching entries in $[[UC1]]$,
    and the merge of matching entries.

@@

\lemUnifMergeSoundness*
\begin{proof}
    \hfill
    \begin{itemize}
        \item $[[UC1 & UC2]] \subseteq [[UC1]] \cup [[UC2]]$\\
        By definition, 
        $[[UC1 & UC2]]$ consists of three parts:
        entries of $[[UC1]]$ that do not have matching entries of $[[UC2]]$,
        entries of $[[UC2]]$ that do not have matching entries of $[[UC1]]$,
        and the merge of matching entries.

@@

\corUnifMergeSoundness*
\begin{proof}
    It is clear that since $[[UC = UC1 ∪ UC2]]$ (by \cref{lemma:unif-merge-soundness}),
    and being normalized means that all entries are normalized,
    $[[UC]]$ is a normalized unification constraint.
    Analogously, $[[Θ ⊢ UC]] = [[UC1 ∪ UC2]]$ holds immediately, 
    since $[[Θ ⊢ UC1]]$ and $[[Θ ⊢ UC2]]$.

@@

\lemUnifEntryMergeCompleteness*
\begin{proof}
    Let us consider the shape of $[[ucE1]]$ and $[[ucE2]]$.
    \begin{caseof}
        \item $[[ucE1]]$ is $[[pua :≈ iQ1]]$ and $[[ucE2]]$ is $[[pua :≈ iQ2]]$.
            Then $[[Γ ⊢ iP : ucE1]]$ means $[[Γ ⊢ iP ≈ iQ1]]$, 
            and $[[Γ ⊢ iP : ucE2]]$ means $[[Γ ⊢ iP ≈ iQ2]]$.
            Then by transitivity of equivalence (\cref{corollary:equivalence-transitivity}),
            $[[Γ ⊢ iQ1 ≈ iQ2]]$, which means $[[nf(iQ1) = nf(iQ2)]]$ by
            \cref{lemma:subt-equiv-algorithmization}.
            Hence, \ruleref{\ottdruleSCMEPEqEqLabel} applies to infer
            $[[Γ ⊢ ucE1 & ucE2 = ucE2]]$, and $[[Γ ⊢ iP : ucE2]]$ holds by assumption.
        \item $[[ucE1]]$ is $[[nua :≈ iN1]]$ and $[[ucE2]]$ is $[[nua :≈ iM2]]$.
            The proof is symmetric.
    \end{caseof}
\end{proof}

\lemUnifMergeCompleteness*
\begin{proof}
    The proof repeats the proof of \cref{lemma:merge-completeness}
    for cases 
    uses \cref{lemma:unif-entry-merge-completeness} instead of \cref{lemma:entry-merge-completeness}.
\end{proof}

### 2023-11-13 proofs/tex/unification-lemmas.tex
Restructure
Restructure proofs

\begin{observation}[Unification is deterministic]
    \label{obs:unif-deterministic}
    \hfill
    \begin{itemize}
        \item [$+$] If $[[Γ ; Θ ⊨ uP ≈u iQ ⫤ UC]]$
            and $[[Γ ; Θ ⊨ uP ≈u iQ ⫤ UC']]$ then $[[UC = UC']]$.
        \item [$-$] If $[[Γ ; Θ ⊨ uN ≈u iM ⫤ UC]]$
            and $[[Γ ; Θ ⊨ uN ≈u iM ⫤ UC']]$ then $[[UC = UC']]$.
    \end{itemize}
\end{observation}
\begin{proof}
    We prove it by mutual structural induction on 
    $[[Γ ; Θ ⊨ uP ≈u iQ ⫤ UC]]$ and $[[Γ ; Θ ⊨ uN ≈u iM ⫤ UC']]$.
    Let us consider the positive case, since the negative case is symmetric.

@@

\begin{lemma}[Soundness of Unification] \label{lemma:unification-soundness}
    \hfill
    \begin{itemize}
        \item [$+$] For normalized $[[uP]]$ and $[[iQ]]$ such that 
        $[[Γ ; dom(Θ) ⊢ uP]]$ and $[[Γ ⊢ iQ]]$,\\ 
        if $[[Γ ; Θ ⊨ uP ≈u iQ ⫤ UC]]$ then 
        $[[Θ ⊢ UC : uv uP]]$ and for any normalized $[[uσ]]$ 
        such that $[[ Θ ⊢ uσ : lift UC ]]$, $[[ [uσ]uP = iQ ]]$.

        \item [$-$] For normalized $[[uN]]$ and $[[iM]]$ such that
        $[[Γ ; dom(Θ) ⊢ uN]]$ and $[[Γ ⊢ iM]]$,\\
        if $[[Γ ; Θ ⊨ uN ≈u iM ⫤ UC]]$ then 
        $[[Θ ⊢ UC : uv uN]]$ and for any normalized $[[uσ]]$ such that
        $[[ Θ   ⊢ uσ : lift UC ]]$, $[[ [uσ]uN = iM ]]$.
    \end{itemize}
\end{lemma}
\begin{proof}
    We prove by induction on the derivation of 
    $[[ Γ ; Θ ⊨ uN ≈u iM ⫤ UC ]]$ and mutually $[[Γ ; Θ ⊨ uP ≈u iQ ⫤ UC]]$.
    Let us consider the last rule forming this derivation. 
    \begin{caseof}
        \item \ruleref{\ottdruleUNVarLabel}, then $[[uN]] = [[α⁻]] = [[iM]]$.
        The resulting unification constraint is empty: $[[UC]] = [[·]]$.
        It satisfies $[[Θ ⊢ UC : ·]]$ vacuously, and $[[ [us]α⁻ = α⁻ ]]$, that is $[[ [us]uN = iM ]]$.

@@

        By applying the induction hypothesis to $[[Γ ; Θ ⊨ uP ≈u iQ ⫤ UC1]]$,
        we have:
        \begin{itemize}
            \item $[[Θ ⊢ UC1 : uv uP]]$,
            \item for any $(Θ  ⊢ lift UC1) ⊢ uσ'$, $[[ [uσ']uP = iQ ]]$.
        \end{itemize}
        By applying it to $[[Γ ; Θ ⊨ uN' ≈u iM' ⫤ UC2]]$, we have:
        \begin{itemize}
            \item $[[Θ ⊢ UC2 : uv uN']]$,
            \item for any $[[ Θ  ⊢ uσ' : lift UC2 ]]$, $[[ [uσ']uN' = iM' ]]$.
        \end{itemize}

@@

\begin{lemma}[Completeness of Unification] \label{lemma:unification-completeness}
    \hfill
    \begin{itemize}
        \item [$+$] For normalized $[[uP]]$ and $[[iQ]]$ such that
        $[[Γ ; dom(Θ) ⊢ uP]]$ and $[[Γ ⊢ iQ]]$, 
        suppose that there exists $[[Θ ⊢ uσ : uv(uP)]]$ such that $[[ [uσ]uP = iQ ]]$,
        then $[[Γ ; Θ ⊨ uP ≈u iQ ⫤ UC]]$ for some $[[UC]]$.

        \item [$-$] For normalized $[[uN]]$ and $[[iM]]$ such that
        $[[Γ ; dom(Θ) ⊢  uN]]$ and $[[Γ ⊢ iM]]$,
        suppose that there exists $[[Θ ⊢ uσ : uv(uN)]]$ such that $[[ [uσ]uN = iM ]]$,
        then $[[Γ ; Θ ⊨ uN ≈u iM ⫤ UC]]$ for some $[[UC]]$.
   \end{itemize}
\end{lemma}
\begin{proof}
    We prove it by induction on the structure of $[[uP]]$ and mutually, $[[uN]]$.
    \begin{caseof}
        \item $[[uN]] = [[α̂⁻]]$\\
            $[[Γ ; dom(Θ) ⊢  α̂⁻]]$ means that $[[ α̂⁻[Δ] ]] \in [[Θ]]$ for some $[[Δ]]$.

>>>>

\obsUnifDet*
\begin{proof}
    We prove it by mutual structural induction on 
    $[[Γ ; Θ ⊨ uP ≈u iQ ⫤ UC]]$ and $[[Γ ; Θ ⊨ uN ≈u iM ⫤ UC']]$.
    Let us consider the positive case only since the negative case is symmetric.

@@

\lemmaUnificationSoundness*
\begin{proof}
    We prove by induction on the derivation of 
    $[[ Γ ; Θ ⊨ uN ≈u iM ⫤ UC ]]$ and mutually $[[Γ ; Θ ⊨ uP ≈u iQ ⫤ UC]]$.
    Let us consider the last rule forming this derivation. 
    \begin{caseof}
        \item \ruleref{\ottdruleUNVarLabel}, then $[[uN]] = [[α⁻]] = [[iM]]$.
        The resulting unification constraint is empty: $[[UC]] = [[·]]$.
        It satisfies $[[Θ ⊢ UC : ·]]$ vacuously, and $[[ [us]α⁻ = α⁻ ]]$, that is $[[ [us]uN = iM ]]$.

@@

        By applying the induction hypothesis to $[[Γ ; Θ ⊨ uP ≈u iQ ⫤ UC1]]$,
        we have:
        \begin{itemize}
            \item $[[Θ ⊢ UC1 : uv uP]]$,
            \item for any $[[Θ ⊢ uσ' : lift UC1]]$, $[[ [uσ']uP = iQ ]]$.
        \end{itemize}
        By applying it to $[[Γ ; Θ ⊨ uN' ≈u iM' ⫤ UC2]]$, we have:
        \begin{itemize}
            \item $[[Θ ⊢ UC2 : uv uN']]$,
            \item for any $[[ Θ  ⊢ uσ' : lift UC2 ]]$, $[[ [uσ']uN' = iM' ]]$.
        \end{itemize}

@@

\lemmaUnificationCompleteness*
\begin{proof}
    We prove it by induction on the structure of $[[uP]]$ and mutually, $[[uN]]$.
    \begin{caseof}
        \item $[[uN]] = [[α̂⁻]]$\\
            $[[Γ ; dom(Θ) ⊢  α̂⁻]]$ means that $[[ α̂⁻[Δ] ]] \in [[Θ]]$ for some $[[Δ]]$.

### 2023-11-13 proofs/tex/upgrade-lemmas.tex
Restructure proofs

\begin{observation}[Upgrade is deterministic]
    \label{obs:upgrade-deterministic}
    Assuming $[[iP]]$ is well-formed in $[[Γ ⊆ Δ]],$\\
    if $[[upgrade Γ ⊢ iP to Δ = iQ]]$ and $[[upgrade Γ ⊢ iP to Δ = iQ']]$ are defined 
    then $[[iQ = iQ']]$.
\end{observation}
\begin{proof}
    It follows directly from \cref{obs:lub-deterministic},
    and the convention that the fresh variables are chosen by a fixed deterministic algorithm
    (\cref{sec:fresh-selection}).
\end{proof}

\begin{lemma}[Soundness of Upgrade]\label{lemma:upgrade-soundness}
    Assuming $[[iP]]$ is well-formed in $[[Γ = Δ, pnas]]$,
    if $[[upgrade Γ ⊢ iP to Δ = iQ]]$
    then
    \begin{enumerate}
        \item $[[Δ ⊢ iQ]]$
        \item $[[Γ ⊢ iQ ≥ iP]]$
    \end{enumerate}
\end{lemma}
\begin{proof}
    By inversion, $[[upgrade Γ ⊢ iP to Δ = iQ]]$ means that 
    for fresh $[[pnbs]]$ and $[[pncs]]$,
    $[[Δ, pnbs, pncs ⊨ [pnbs/pnas]iP ∨ [pncs/pnas]iP = iQ]]$.
    Then by the soundness of the least upper bound (\cref{lemma:lub-soundness}),
    \begin{enumerate}
        \item $[[Δ, pnbs, pncs ⊢ iQ]]$, 
        \item $[[Δ, pnbs, pncs ⊢ iQ ≥ [pnbs/pnas]iP]]$, and 
        \item $[[Δ, pnbs, pncs ⊢ iQ ≥ [pncs/pnas]iP]]$.
    \end{enumerate}

@@

\begin{lemma}[Completeness and Initiality of Upgrade] \label{lemma:upgrade-completeness}
    The upgrade returns the least $[[Γ]]$-supertype of $[[iP]]$ well-formed in $[[Δ]]$.
    Assuming $[[iP]]$ is well-formed in $[[Γ = Δ, pnas]],$\\
    For any $[[iQ']]$ such that 
    \begin{enumerate}
        \item $[[Δ ⊢ iQ']]$ and
        \item $[[Γ ⊢ iQ' ≥ iP]]$,
    \end{enumerate}

    The result of the upgrade algorithm $[[iQ]]$ exists
    ($[[upgrade Γ ⊢ iP to Δ = iQ]]$) and satisfies $[[Δ ⊢ iQ' ≥ iQ]]$.
\end{lemma}
\begin{proof}

    Let us consider fresh (not intersecting with $[[Γ]]$) $[[pnbs]]$ and $[[pncs]]$.

>>>>

\obsUpgradeDeterminism*
\begin{proof}
    It follows directly from \cref{obs:lub-deterministic},
    and the convention that the fresh variables are chosen by a fixed deterministic algorithm
    (\cref{sec:fresh-selection}).
\end{proof}

\lemmaUpgradeSoundness*
\begin{lemma}[Soundness of Upgrade]\label{lemma:upgrade-soundness}
    Assuming $[[iP]]$ is well-formed in $[[Γ = Δ, pnas]]$,
    if $[[upgrade Γ ⊢ iP to Δ = iQ]]$
    then
    \begin{enumerate}
        \item $[[Δ ⊢ iQ]]$
        \item $[[Γ ⊢ iQ ≥ iP]]$
    \end{enumerate}
\end{lemma}
\begin{proof}
    By inversion, $[[upgrade Γ ⊢ iP to Δ = iQ]]$ means that 
    for fresh $[[pnbs]]$ and $[[pncs]]$,
    $[[Δ, pnbs, pncs ⊨ [pnbs/pnas]iP ∨ [pncs/pnas]iP = iQ]]$.
    Then by the soundness of the least upper bound (\cref{lemma:lub-soundness}),
    \begin{enumerate}
        \item $[[Δ, pnbs, pncs ⊢ iQ]]$, 
        \item $[[Δ, pnbs, pncs ⊢ iQ ≥ [pnbs/pnas]iP]]$, and 
        \item $[[Δ, pnbs, pncs ⊢ iQ ≥ [pncs/pnas]iP]]$.
    \end{enumerate}

@@

\lemmaUpgradeCompleteness*
\begin{proof}
    Let us consider fresh (not intersecting with $[[Γ]]$) $[[pnbs]]$ and $[[pncs]]$.

### 2023-11-13 proofs/tex/wf-algo-lemmas.tex
Restructure proofs

\begin{lemma}[Soundness of algorithmic type well-formedness]
    \label{lemma:wf-algo-soundness}
    \hfill
  \begin{itemize}
    \item[$+$] if $[[Γ ; Ξ ⊢ uP]]$ then $[[fv(uP) ⊆ Γ]]$ and $[[uv(uP) ⊆ Ξ]]$;
    \item[$-$] if $[[Γ ; Ξ ⊢ uN]]$ then $[[fv(uN) ⊆ Γ]]$ and $[[uv(uN) ⊆ Ξ]]$.
  \end{itemize}
\end{lemma}
\begin{proof}
  The proof is analogous to \cref{lemma:wf-soundness}.
  The additional base case is when $[[Γ ; Ξ ⊢ uP]]$ is derived by \ruleref{\ottdruleWFATPUVarLabel},
  and the symmetric negative case.
  In this case, $[[uP]] = [[α̂⁺]]$, and $[[uv(uP)]] = [[{α̂⁺} ⊆ Ξ]]$ by inversion; $[[fv(uP)]] = [[∅ ⊆ Γ]]$ vacuously.
\end{proof}

\begin{lemma}[Completeness of algorithmic type well-formedness]
  \label{lemma:wf-algo-ctxt-equiv}
  In the well-formedness judgment, only used variables matter:
  \begin{itemize}
  \item[$+$] if $[[Γ1 ∩ fv iP]] = [[Γ2 ∩ fv iP]]$
    and $[[Ξ1 ∩ uv uP]] = [[Ξ2 ∩ uv uP]]$ then
    $[[Γ1 ; Ξ1 ⊢ uP]] \iff [[Γ2 ; Ξ2 ⊢ uP]]$, and
  \item[$-$] if $[[Γ1 ∩ fv iN]] = [[Γ2 ∩ fv iN]]$
    and $[[Ξ1 ∩ uv uN]] = [[Ξ2 ∩ uv uN]]$ then
    $[[Γ1 ; Ξ1 ⊢ uN]] \iff [[Γ2 ; Ξ2 ⊢ uN]]$.
  \end{itemize}
\end{lemma}
\begin{proof}
  By mutual structural induction on $[[uP]]$ and $[[uN]]$.
\end{proof}

\begin{lemma}[Variable algorithmization agrees with well-formedness]
  \label{lemma:var-algo-wf}
  \hfill
  \begin{itemize}
    \item[$+$]  $[[Γ, nas ⊢ iP]]$ implies $[[Γ; {nuas} ⊢ [nuas/nas]iP]]$;
    \item[$-$]  $[[Γ, nas ⊢ iN]]$ implies $[[Γ; {nuas} ⊢ [nuas/nas]iN]]$.
  \end{itemize}
\end{lemma}
\begin{proof}
  The proof is a structural induction on $[[Γ, nas ⊢ iP]]$ and mutually, on $[[Γ, nas ⊢ iN]]$.
  Notice that the substitutions commute with all the constructors,
  providing the step of the induction. 
\end{proof}

\begin{lemma}[Variable dealgorithmization agrees with well-formedness]
  \label{lemma:var-dealgo-wf}
  \hfill
  \begin{itemize}
    \item[$+$]  $[[Γ; {nuas} ⊢ uP]]$ implies $[[Γ, nas ⊢ [nas/nuas]iP]]$;
    \item[$-$]  $[[Γ; {nuas} ⊢ uN]]$ implies $[[Γ, nas ⊢ [nas/nuas]iN]]$.
  \end{itemize}
\end{lemma}
\begin{proof}
  As for \cref{lemma:var-algo-wf}, the proof is a structural induction on 
  $[[Γ; {nuas} ⊢ uP]]$ and mutually, on $[[Γ; {nuas} ⊢ uN]]$.
\end{proof}

\begin{corollary}[Well-formedness Algorithmic Context Weakening]
  \label{lemma:wf-weakening-algo}
  Suppose that $[[Γ1 ⊆ Γ2]]$,
  and $[[Ξ1 ⊆ Ξ2]]$. Then
  \begin{itemize}
    \item[$+$] if $[[Γ1 ; Ξ1 ⊢ uP]]$ implies $[[Γ2 ; Ξ2 ⊢ uP]]$,
    \item [$-$] if $[[Γ1 ; Ξ1 ⊢ uN]]$ implies $[[Γ2 ; Ξ2 ⊢ uN]]$.
  \end{itemize}
\end{corollary}
\begin{proof}
  By \cref{lemma:wf-algo-soundness},
  $[[Γ1; Ξ1 ⊢ uP]]$ implies $[[fv(uP) ⊆ Γ1 ⊆ Γ2]]$
  and $[[uv(uP) ⊆ Ξ1 ⊆ Ξ2]]$,
  and thus, $[[fv(uP)]] = [[fv(uP) ∩ Γ1]] = [[fv(uP) ∩ Γ2]]$, 
  and $[[uv(uP)]] = [[uv(uP) ∩ Ξ1]] = [[uv(uP) ∩ Ξ2]]$.
  Then by \cref{lemma:wf-algo-ctxt-equiv}, $[[Γ2; Ξ2 ⊢ uP]]$. 
  The negative case is symmetric.
\end{proof}

>>>>

\lemmaWfAlgoSoundness*
\begin{proof}
  The proof is analogous to \cref{lemma:wf-soundness}.
  The additional base case is when $[[Γ ; Ξ ⊢ uP]]$ is derived by \ruleref{\ottdruleWFATPUVarLabel},
  and the symmetric negative case.
  In this case, $[[uP]] = [[α̂⁺]]$, and $[[uv(uP)]] = [[{α̂⁺} ⊆ Ξ]]$ by inversion; $[[fv(uP)]] = [[∅ ⊆ Γ]]$ vacuously.
\end{proof}

\lemmaWfAlgoCtxtEquiv*
\begin{proof}
  By mutual structural induction on $[[uP]]$ and $[[uN]]$.
\end{proof}

\lemmaVarAlgoWf*
\begin{proof}
  The proof is a structural induction on $[[Γ, nas ⊢ iP]]$ and mutually, on $[[Γ, nas ⊢ iN]]$.
  Notice that the substitutions commute with all the constructors,
  providing the step of the induction. 
\end{proof}

\lemmaVarDealgoWf*
\begin{proof}
  As for \cref{lemma:var-algo-wf}, the proof is a structural induction on 
  $[[Γ; {nuas} ⊢ uP]]$ and mutually, on $[[Γ; {nuas} ⊢ uN]]$.
\end{proof}

\corollaryWfWeakeningAlgo*
\begin{proof}
  By \cref{lemma:wf-algo-soundness},
  $[[Γ1; Ξ1 ⊢ uP]]$ implies $[[fv(uP) ⊆ Γ1 ⊆ Γ2]]$
  and $[[uv(uP) ⊆ Ξ1 ⊆ Ξ2]]$,
  and thus, $[[fv(uP)]] = [[fv(uP) ∩ Γ1]] = [[fv(uP) ∩ Γ2]]$, 
  and $[[uv(uP)]] = [[uv(uP) ∩ Ξ1]] = [[uv(uP) ∩ Ξ2]]$.
  Then by \cref{lemma:wf-algo-ctxt-equiv}, $[[Γ2; Ξ2 ⊢ uP]]$. 
  The negative case is symmetric.
\end{proof}
